251 MA

### 2023-03-02 code/process.Rmd
minor updates

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
library(metafor)
library(esc)
library(here)
library(brms)
library(rstan)

@@

```{r, eval=F}
library(googledrive)

f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/1UT6KLRujn6iEQ_s01_4yNfFYqc7hAWTpB-t9mdDp0O8/edit#gid=0")
googledrive::drive_download(f, path="raw_data.xlsx", overwrite=T)

@@

```{r}
d <- readxl::read_xlsx("raw_data.xlsx", sheet="aligned data", skip=1) |>

  select(target_lastauthor_year, sensitivity, include,
         status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, target_ES_value,
         same_dir,
         replication_N, replication_test, replication_raw_stat, replication_pvalue, replication_ES_type, replication_ES_value,
         replicated_instructor_code, replicated_report_code, adjudicated_replication_code)

@@

@@

- "done" -- fully coded, can be used for whatever is specified in other column

- "ES_direction" -- we don't have the direction coded

- "ask" -- might be salvageable, but I have questions about coding

- "unusable" -- got as far as I can, and it does not have complete descriptives

- "missing" -- student didn't finish or we don't have write-up

- "non-experiment" -- student replicated something that was not an experiment

- "reproduction" -- student did a reproduction and not replication

```{r}
d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))

```{r}
#helper function for pooling when needed
pool_m_sd <- function(m1, sd1, n1, m2, sd2, n2){
  m=(m1*n1+m2*n2)/(n1+n2)
  var=(n1*(sd1**2+m1**2)+n2*(sd2**2+m2**2))/(n1+n2)-m**2
  sd=sqrt(var)
  return(c(m,sd))

}
```
# Parsing

@@

```{r}
# considered using the effectsize package but afaik we don't care about estimating CI's here and there were optim problems with that

parse_t <- function(tval, within_between) {
  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pt(q=val, df=df, lower.tail=FALSE)*2
  d_calc=NA
  N_from_df=NA
  if(within_between=="between"){
    d_calc=2*val/(sqrt(df+2)) # this is a simplification for equal groups
    N_from_df=df+2 # between so add 2
  }
  else{
    d_calc=val/sqrt(df+1)
    N_from_df=df+1
  }
  se=4/N_from_df+d_calc**2/(2*N_from_df)
  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
}
```

```{r}
parse_f <- function(fval, within_between){
  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
  d_calc=NA
  N_from_df=df_1+df_2+1
  if(!is.na(df_1)&&df_1==1){
    if(within_between=="between"){
      d_calc=2*sqrt(val)/sqrt(N_from_df) # if there's just two groups, then F=t**2 and we can use the t-test thingy
    }
    else{
      d_calc=sqrt(val)/sqrt(df_2)
    }
   se=4/N_from_df+d_calc**2/(2*N_from_df)
  }
  else if(!is.na(df_1)){
    d_calc=NA
    se=NA
  }

  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
}
```

```{r}
# for comparison between proportions 
#ex <- "prob: 13 / 14 , 2 / 14"
parse_prop <- function(propval){
  val <- str_extract_all(propval, "[0-9]+")[[1]]
  num1 <- val[1] |> as.numeric()
  den1 <- val[2] |> as.numeric()
  num2 <- val[3] |> as.numeric()
  den2 <- val[4] |> as.numeric()
  est1 <- num1/den1
  est1_var <- est1*(1-est1)/den1
  est2 <- num2/den2
  est2_var <- est2*(1-est2)/den2
  diff <- est1-est2
  diff_var <- est1_var+est2_var
  return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=diff, "SE"=sqrt(diff_var)))
}
#parse_prop(ex)

```{r}
# for one proportion
#ex <- "raw prop : 10 / 18"
parse_raw_prop <- function(propval){
  val <- str_extract_all(propval, "[0-9]+")[[1]]
  num1 <- val[1] |> as.numeric()
  den1 <- val[2] |> as.numeric()
  est1 <- num1/den1
  est1_var <- est1*(1-est1)/den1
   return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=est1, "SE"=sqrt(est1_var)))
}
#parse_raw_prop(ex)
```

```{r}
parse_mean_ci <- function(mci,within_between,n){
  # parsing 
  cond1=str_extract(mci, "m1.*\\],")
  cond2=str_extract(mci, "m2.*\\]")
  m1=str_extract(cond1, "m1=.*\\[") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\[") |> str_sub(4,-2) |> as.numeric()
  low1=str_extract(cond1, "\\[.*,.") |> str_sub(2,-3) |> as.numeric()
  low2=str_extract(cond2, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high1=str_extract(cond1, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  # calculations 
  se1=high1-low1/(2*1.96)
  se2=high2-low2/(2*1.96)
  per_group_n=ifelse(within_between=="within",n, n/2)
  sd1=se1*sqrt(per_group_n-1) # assume equal groups
  sd2=se2*sqrt(per_group_n-1)
  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
  se_pool=sd_pool/sqrt(n-1)
  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
  tval=(m1-m2)/se_pool |> abs()
  df=ifelse(within_between=="within", n-1, n-2)
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
}
```

```{r}
parse_mean_sd <- function(msd,within_between,n){
  cond1=str_extract(msd, "m1.*\\),")
  cond2=str_extract(msd, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  #
  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
  se_pool=sd_pool/sqrt(n-1)
  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
  tval=(m1-m2)/se_pool |> abs()
  df=ifelse(within_between=="within", n-1, n-2)
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
}

```{r}
parse_mean_se <- function(mse,within_between,n){
  cond1=str_extract(mse, "m1.*\\),")
  cond2=str_extract(mse, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()

  per_group_n=ifelse(within_between=="within",n, n/2)
  sd1=se1*sqrt(per_group_n-1) # assume equal groups
  sd2=se2*sqrt(per_group_n-1)
  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
  se_pool=sd_pool/sqrt(n-1)
  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
  tval=(m1-m2)/se_pool |> abs()
  df=ifelse(within_between=="within", n-1, n-2)
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
}

parse_beta_se <- function(raw_stat){
    beta=str_extract(raw_stat, "b=.*\\(") |> str_sub(3,-2) |> as.numeric()
    se=str_extract(raw_stat, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
    #zval=beta/se
    #pval=2*pnorm(zval, lower.tail=F)
return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
}

parse_beta_ci <- function(raw_stat){
  beta=str_extract(raw_stat, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
  low=str_extract(raw_stat, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high=str_extract(raw_stat, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se=high-low/(2*1.96)
 #zval=beta/se
    #pval=2*pnorm(zval, lower.tail=F)
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=beta, "SE"=se))
}

#this is just to deal with yang2018 where we have d's given and bci
#ex <- "d: 1.40 ; bci: b=1.72 [1.44, 2.00]"
parse_dbci <- function(raw_stat){
  bci = str_extract(raw_stat, ";.*") |> str_sub(2,-1)
  beta=str_extract(bci, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
  low=str_extract(bci, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high=str_extract(bci, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se=high-low/(2*1.96)

  dval = str_extract(raw_stat, ".*;") |> str_sub(3,-2) |> as.numeric()
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=dval, "N_calc"=NA, "ES"=beta, "SE"=se))
}
#parse_dbci(ex)

do_blanks <- function(){
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=NA, "SE"=NA))
}
do_parsing=function(raw_stat, within_between,n){
  if (is.na(raw_stat)) {return (do_blanks())}
  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
  if (str_sub(raw_stat,1,4)=="prop"){return(parse_prop(raw_stat))}
  if (str_sub(raw_stat,1,7)=="rawprop"){return(parse_raw_prop(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_ci(raw_stat))}
  if (str_sub(raw_stat, 1,1)=="d"){return(parse_dbci(raw_stat))}

  return (do_blanks())
}
```

test <- d_val |> 
  mutate(target_raw_stat=gsub(" ","",target_raw_stat),
         target=pmap(list(target_raw_stat, within_between,target_N), do_parsing),
         replication_raw_stat=gsub(" ","",replication_raw_stat),
         rep=pmap(list(replication_raw_stat, within_between,replication_N), do_parsing)) |> 
  unnest(cols=c(target, rep), names_sep="_") |> 
  rowwise()

@@

```{r}
library(metafor)

d_es <-  test |> 
  mutate(target_d_calc=abs(target_d_calc),
         target_ES=abs(target_ES),
         rep_d_calc=case_when(
           same_dir=="yes" ~ abs(rep_d_calc),
           same_dir=="no" ~-abs(rep_d_calc),
           T ~ as.numeric(NA)
          ),
         rep_ES=case_when(
           same_dir=="yes" ~ abs(rep_ES),
           same_dir=="no" ~-abs(rep_ES),
           T ~ as.numeric(NA)
         ))

```{r}
do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)){
    return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
  }
  return(NA)
}

do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)){
    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
  }
  return(NA)
}

do_subjective_rep <- function(replicated_instructor_code, replicated_report_code, adjudicated_replication_code){
  if (is.na(replicated_instructor_code)){return(as.numeric(NA))}
  if (is.na(replicated_report_code)){return(as.numeric(NA))}
  if (replicated_instructor_code==replicated_report_code){ return(replicated_instructor_code)}
  if (!is.na(adjudicated_replication_code)){return (adjudicated_replication_code)}
  return(as.numeric(NA))
}
d_es_predInt <- d_es |> 
  rowwise() |> 
         mutate(
           predInt=do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
           p_orig=do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
           sub_rep= do_subjective_rep(replicated_instructor_code, replicated_report_code, adjudicated_replication_code))

# viz SMD
```{r}

d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_orig))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="p_orig", x="Original SMD", y="Replication SMD")

d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=predInt))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="rep in predInt", x="Original SMD", y="Replication SMD")

d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="subrep", x="Original SMD", y="Replication SMD")

```
# viz ES any scale 
```{r}
library(ggstance)
d_es_predInt |> ggplot(aes(x=target_ES, 
                           xmin=target_ES-target_SE*1.96,
                           xmax=target_ES+target_SE*1.96, 
                           y=rep_ES,
                           ymin=rep_ES-rep_SE*1.96,
                           ymax=rep_ES+rep_SE*1.96,
                           color=p_orig))+
  geom_linerange(alpha=.5)+
  geom_linerangeh(alpha=.5)+
    geom_point()+
  coord_cartesian(xlim=c(-1,12), ylim=c(-1,12))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="p_orig", x="Original ES", y="Replication ES")

@@

strong_priors <- c(set_prior("horseshoe(3, par_ratio=.33)", class="b"),
            set_prior("normal(0,.5)", class="sd"),
            set_prior("lkj(1)", class="cor"))
tier1_subjective_strong_prior<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        family="cumulative", # runs on 1-5 data
                        data=data_tier1,
                        file=here(model_location, "tier1_subjective_prior"),
                        prior=strong_priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr"
                        )
```

strong_priors_no_ranef <- c(set_prior("horseshoe(3, par_ratio=.33)", class="b"),
            set_prior("normal(0,.5)", class="sd"))
tier1_subjective_strong_prior<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (1 | academic_year),
                        family="cumulative", # runs on 1-5 data
                        data=data_tier1,
                        file=here(model_location, "tier1_subjective_prior_no_ranef"),
                        prior=strong_priors_no_ranef, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr"
                        )
```

@@

                        )
library(glmnet)

predictors <- data_tier1 |> select(z_pub_year, open_data, open_mat, stanford, change_platform, 
                          z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
library(metafor)
library(esc)
library(here)
library(brms)
library(rstan)
library(googledrive)
library(glmnet)

@@

Download

```{r, eval=F}
f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/1UT6KLRujn6iEQ_s01_4yNfFYqc7hAWTpB-t9mdDp0O8/edit#gid=0")
googledrive::drive_download(f, path=here("data","raw_data.xlsx"), overwrite=T)

@@

Read in cache.

```{r}
d <- readxl::read_xlsx(here("data","raw_data.xlsx"), 
                       sheet="aligned data", skip=1) |> 
  select(target_lastauthor_year, sensitivity, include,
         status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, 
         target_ES_value, same_dir, replication_N, # replication_test
         replication_raw_stat, replication_pvalue, replication_ES_type, 
         replication_ES_value, replicated_instructor_code, replicated_report_code,
         adjudicated_replication_code)

@@

Counts.

@@

- "done" -- fully coded, can be used for whatever is specified in other column 
- "ES_direction" -- we don't have the direction coded 
- "ask" -- might be salvageable, but I have questions about coding
- "unusable" -- got as far as I can, and it does not have complete descriptives
- "missing" -- student didn't finish or we don't have write-up
- "non-experiment" -- student replicated something that was not an experiment
- "reproduction" -- student did a reproduction and not replication

```{r}
d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))
```

# Parsing

@@

```{r}
source(here("code","helper","parse_stats.R"))
```

```{r}
test <- d_val |> 
  mutate(target_raw_stat=gsub(" ","",target_raw_stat),
         target=pmap(list(target_raw_stat, within_between,target_N), do_parsing),
         replication_raw_stat=gsub(" ","",replication_raw_stat),
         rep=pmap(list(replication_raw_stat, within_between,replication_N), do_parsing)) |> 
  unnest(cols=c(target, rep), names_sep="_") |> 
  rowwise()
```

@@

```{r}
source(here("code","helper","stats.R"))
```

Compute prediction intervals and p_orig.

```{r}
d_es_predInt <- d_es |> 
  rowwise() |> 
  mutate(predInt = do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
         p_orig = do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
         sub_rep = do_subjective_rep(replicated_instructor_code, 
                                     replicated_report_code, 
                                     adjudicated_replication_code))
```

# viz SMD

First pass plots.

```{r}
d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_orig))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="p_orig", x="Original SMD", y="Replication SMD")

d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=predInt))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="rep in predInt", x="Original SMD", y="Replication SMD")
```

Working more on the visualization with subjective rep status.

```{r}
d_es_predInt |> 
  filter(target_d_calc < 5, rep_d_calc < 5) |>
  ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
  geom_point() +
  geom_abline(slope=1, intercept=0, lty = 2)+
  geom_smooth(method = "lm") + 
  geom_hline(yintercept = 0, lty = 2)+
  scale_color_viridis(discrete=F, direction = -1, 
                      name = "Subjective Replication Success")+
  labs(color="subrep", x="Original SMD", y="Replication SMD") + 
  theme(legend.position = "bottom")
```

```{r}
library(ggstance)
d_es_predInt |> ggplot(aes(x=target_ES, 
                           xmin=target_ES-target_SE*1.96,
                           xmax=target_ES+target_SE*1.96, 
                           y=rep_ES,
                           ymin=rep_ES-rep_SE*1.96,
                           ymax=rep_ES+rep_SE*1.96,
                           color=p_orig))+
  geom_linerange(alpha=.5)+
  geom_linerangeh(alpha=.5)+
  geom_point()+
  coord_cartesian(xlim=c(-1,12), ylim=c(-1,12))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="p_orig", x="Original ES", y="Replication ES")

@@

strong_priors <- c(set_prior("horseshoe(3, par_ratio=.33)", class="b"),
                   set_prior("normal(0,.5)", class="sd"),
                   set_prior("lkj(1)", class="cor"))

tier1_subjective_strong_prior <- brm(sub_rep ~ z_pub_year +
                                       subfield + open_data +  
                                       open_mat + stanford + change_platform + 
                                       z_log_ratio_ss + is_within + 
                                       single_vignette + z_log_sample + 
                                       z_log_trials + 
                                       (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                                     family="cumulative", # runs on 1-5 data
                                     data=data_tier1,
                                     file=here(model_location, "tier1_subjective_prior"),
                                     prior=strong_priors, 
                                     control=list(adapt_delta=.99),
                                     backend="cmdstanr"
)
```

@@

)
```

regularized
```{r}
predictors <- data_tier1 |> select(z_pub_year, open_data, open_mat, stanford, change_platform, 
                                   z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)

@@

# Random exploratory analyses

## Correlations

```{r}
sub_cor <- function(var, stat = "estimate") {
  if (stat == "estimate") {
    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$estimate
  } else {
    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$p.value
  }
}

preds <- c("z_pub_year", "open_data",  "open_mat", "stanford", "change_platform", 
           "z_log_ratio_ss", "is_within", "single_vignette", "z_log_sample", 
           "z_log_trials")

cors <- tibble(preds = preds) |>
  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
         p = sapply(preds, function(x) sub_cor(x, stat = "p")))

knitr::kable(cors, digits = 3)
```

## Principal components

Principal components are not very interpretable.

```{r}
pcs <- select(data_tier1, 
              z_pub_year, open_data,  open_mat, stanford, change_platform, 
              z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |>
  princomp()

summary(pcs)
pcs$loadings
plot(pcs)
biplot(pcs)
```

## Model exploration

```{r}
mod <- lm(sub_rep ~ z_pub_year + subfield + open_data + open_mat + 
            stanford + change_platform + 
            z_log_ratio_ss + is_within + 
            single_vignette + z_log_sample + z_log_trials,
          data = data_tier1 )
summary(mod)
```

Repeating regularized

```{r}
predictors <- data_tier1 |> 
  select(z_pub_year, open_data, open_mat, stanford, change_platform, 
         z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials) |>
  as.data.frame() |>
  as.matrix()

lasso_linear <- cv.glmnet(predictors, data_tier1$sub_rep, 
                          family="gaussian", alpha=1)

coef(lasso_linear, s = "lambda.min")
coef(lasso_linear, s = "lambda.1se")
```

## Bayesian tinkering

Let's try super strong priors, consolidating a few very highly correlated variables.

```{r}
normal_priors <- c(set_prior("horseshoe(3)", class="b"),
                   set_prior("normal(0,.5)", class="sd"))

brm(sub_rep ~ z_pub_year + subfield + open_data + open_mat + stanford + change_platform + z_log_ratio_ss + is_within + single_vignette + z_log_sample +  z_log_trials + 
      (1 | academic_year),
    # family = "linear", # runs on 1-5 data
    data = data_tier1,
    prior = normal_priors, 
    iter = 10000, warmup = 2000,
    control = list(adapt_delta=.99),
    backend = "cmdstanr")
```

And let's see if it's the link

```{r}
normal_priors <- c(set_prior("horseshoe(3)", class="b"),
                   set_prior("normal(0,.5)", class="sd"))

# make it in the .005 - .995 range
data_tier1$sub_rep01 <- ((data_tier1$sub_rep-1)/5) * .99 + .005

brm(sub_rep01 ~ z_pub_year + subfield + open_data + open_mat + stanford + change_platform + z_log_ratio_ss + is_within + single_vignette + z_log_sample +  z_log_trials + 
      (1 | academic_year),
    family = "beta", # runs on 1-5 data
    data = data_tier1,
    prior = normal_priors, 
    iter = 10000, warmup = 2000,
    control = list(adapt_delta=.99),
    backend = "cmdstanr")
```

## Models of clusters of predictors

```{r}
mod <- lm(sub_rep ~ 
            is_within + 
            single_vignette +  z_log_trials,
          data = data_tier1 )
summary(mod)
```
